### 2023-09-23 sections/selected-training.tex
Update selected-training.tex
LPPL v1.3c

\begin{cvhonors}
\cvconf
{Research Data Workshop IT Centre at the University of Oxford} 
{Oxford, UK}
{2019}
\end{cvhonors}

@@

\begin{cvhonors}
\cvconf
{Longitudinal Networks with RSiena Workshop at the P Universidad Cat\'olica}
{Santiago, Chile}
{2018}
\end{cvhonors}

@@

\begin{cvhonors}
\cvconf
{Universidad de Santiago Winter School for Academics}
{Santiago, Chile}
{2016}
\end{cvhonors}

@@

\begin{cvhonors}
\cvconf
{Nuffield-USACH CEES Experimental Summer School}
{Santiago, Chile}
{2016}
\end{cvhonors}

@@

\begin{cvhonors}
\cvconf
{Universidad de Santiago Winter School for Academics}
{Santiago, Chile}
{2015}
\end{cvhonors}

@@

\begin{cvhonors}
\cvconf
{Latin American Political Science Association Methodological School}
{Lima, Peru}
{2015}
\end{cvhonors}

@@

\begin{cvhonors}
\cvconf
{Universidad Cat\'olica de Uruguay Winter School in Methods and Data Analysis}
{MVD, Uruguay}
{2015}
\end{cvhonors}

@@

\begin{cvhonors}
\cvconf
{P Universidad Ca\'olica Summer School in Mixed Methods}
{Santiago, Chile}
{2014}
\end{cvhonors}

>>>>

\begin{cvhonors}
\cvconf
{Research Data Workshop IT Centre at the University of Oxford} 
{Oxford, GBR}
{2019}
\end{cvhonors}

@@

\begin{cvhonors}
\cvconf
{Longitudinal Networks with RSiena Workshop at the P Universidad Cat\'olica}
{Santiago, CHL}
{2018}
\end{cvhonors}

@@

\begin{cvhonors}
\cvconf
{Universidad de Santiago Winter School for Academics}
{Santiago, CHL}
{2016}
\end{cvhonors}

@@

\begin{cvhonors}
\cvconf
{Nuffield-USACH CEES Experimental Summer School}
{Santiago, CHL}
{2016}
\end{cvhonors}

@@

\begin{cvhonors}
\cvconf
{Universidad de Santiago Winter School for Academics}
{Santiago, CHL}
{2015}
\end{cvhonors}

@@

\begin{cvhonors}
\cvconf
{Latin American Political Science Association Methodological School}
{Lima, PER}
{2015}
\end{cvhonors}

@@

\begin{cvhonors}
\cvconf
{Universidad Católica de Uruguay Winter School in Methods and Data Analysis}
{Montevideo, URY}
{2015}
\end{cvhonors}

@@

\begin{cvhonors}
\cvconf
{P Universidad Caólica Summer School in Mixed Methods}
{Santiago, CHL}
{2014}
\end{cvhonors}
